Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-03 main.tex
correction
Update on Overleaf.
some constants

    To complete the discussion, we recall by Proposition~\ref{proposition:pullbackestimate} that 
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k-1}
        \| \tilde w \|_{L^{p}(\Delta^n)}
        ,
        \\
        \| \hat g \|_{L^{p}(\Delta^n)}
        &\leq 
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k}
        \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
\end{proof}

@@

We consider the following example domains in two dimensions:
the unit square $\Omega_Q$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{S}$:
\begin{gather*}
    \Omega_{Q} = ( 0,1)^2,
    \qquad 
    \Omega_{L} = (-1,1)^2 \setminus (0,1)^2,
    \\
    \Omega_{S} = (-1,1)^2 \setminus ( [0,1) \times \{0\} ).
\end{gather*}
We consider the triangulations: 
\begin{itemize}
    \item $\calT_{Q}$:  square triangulation with two triangles
    \item $\calT_{L}$:  L-shaped domain triangulation with four triangles
    \item $\calT_{S}$:  Slit domain triangulation, five triangles 
    \item $\calT_{S'}$: Slit domain triangulation, 8 triangles, four of which touch the origin.
\end{itemize}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio & $\grad$ est & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 1.684337597 &               & 1.684337582       & 3.141        & 0.225              & 1.684337545        &  6.928              \\ 
        \hline
        $\calT_{L}$     & 0.822        & 2.904309304 &               & 1.733455376       & 2.895              & 0.322              & 1.733455385              &  7.402              \\ 
        \hline
        $\calT_{S}$     & 0.978        & 3.357380776 &               & 2.170240475       & 2.982              & 0.346              & 2.170240474              &  8.419              \\ 
        \hline
        $\calT_{S'}$    & 0.978        & 3.368675195 &               & 3.368675191       & 4.870              & 0.346              & 3.368675191              & 13.748              \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\ 
        \hline
        $\calT_{C}$     & 0.3177997026 &             &                    &  1.147682616 & 3.611339490040196  \\ 
        \hline
        $\calT_{K}$     & 0.3179254398 &             &                    & 12.73827122  & 91.66905966662563  \\ 
        \hline
        $\calT_{B,5}$   & 1.022627161  &             &                    & 36.7821067   & 35.96824737574127  \\ 
        \hline
        $\calT_{B}$     & 1.022627161  &             &                    & 62.40578125  & 61.02495966269372  \\ 
        \hline
        $\calT_{F}$     & 0.7117133306 &             &                    & 325.7340627  & 18796.92616132183  \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C}$     & 0.2250695032 & 1.147682616 & 5.099236457042005 & 0.1837881324      & 1.5265605865      &  8.30608900893      \\ 
        \hline
        $\calT_{K}$     & 0.2250062929 & 29.14392611 & 129.5249378629681 & 0.1837655124      & 25.68030786       & 139.7449800105412   \\ 
        \hline
        $\calT_{B,5}$   & 0.3315710272 & 160.0052039 & 482.5669036190229 & 0.2330604743      & 160.7339833       & 689.6664212985330   \\ 
        \hline
        $\calT_{B}$     & 0.3315710272 & 572.3519405 & 1726.182004903473 & 0.2330604743      & 510.806374        & 2191.733177984011   \\ 
        \hline
        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

>>>>

    To complete the discussion, we recall by Proposition~\ref{proposition:pullbackestimate} that 
    \begin{align*}
        \| w \|_{L^{p}(T)}
        &\leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \matnorm{ \Jacobian \varphi^{-1} }^{k}
        \| \tilde w \|_{L^{p}(\Delta^n)}
        ,
        \\
        \| \hat g \|_{L^{p}(\Delta^n)}
        &\leq 
        |\det( \Jacobian \varphi^{-1} )|^{\frac 1 p} 
        \matnorm{\Jacobian \varphi}^{k+1}
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{align*}
    It remains to use Lemma~\ref{lemma:measurerelationships}, and the desired inequality is shown. 
\end{proof}

@@

We consider the following example domains in two dimensions:
the unit square $\Omega_Q$, the L-shaped domain $\Omega_L$, and the slit domain $\Omega_{S}$:
\begin{gather*}
    \Omega_{Q} = ( 0,1)^2,
    \qquad 
    \Omega_{L} = (-1,1)^2 \setminus (0,1)^2,
    \\
    \Omega_{S} = (-1,1)^2 \setminus ( [0,1) \times \{0\} ).
\end{gather*}
We consider the triangulations: 
\begin{itemize}
    \item $\calT_{Q}$:  square triangulation with two triangles
    \item $\calT_{L}$:  L-shaped domain triangulation with four triangles
    \item $\calT_{S}$:  Slit domain triangulation, five triangles 
    \item $\calT_{S'}$: Slit domain triangulation, 8 triangles, all of which touch the origin.
    \item $\calT_{S''}$: Slit domain triangulation, 8 triangles, four of which touch the origin.
\end{itemize}

@@

The shelling-based estimate for the Poincar\'e constant of the gradient potential outperforms the estimate in Section~\ref{section:gradient} in our examples where the triangles are not all congruent to each other ($\calT_{L}$ and $\calT_{S,5}$).
That is a result of our implementation, where the face-based reflections are not necessarily onto, which allows for some improved estimates.

\begin{table}[t]
    \centering
    \begin{tabular}{|c||c|c|c|c|c||c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio & $\grad$ est & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.9040624834 &               & 0.904062477        & 3.141        & 0.225              & 1.339553527              &  6.928              \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381225711 &               & 1.421249625        & 2.895              & 0.322              & 2.505543143         &  7.402              \\
        \hline
        $\calT_{L'}$     & 0.822        & 2.391924501 &               & 2.391924492        & 2.895              & 0.322              & 4.053039867        &  7.402              \\
        \hline
        $\calT_{S,5}$     & 0.978        & 2.752696283 &               & 1.779367097       & 2.982              & 0.346              & 3.717588832       &  8.419              \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131764309 &               & 3.131764307       & 4.870              & 0.346              & 5.453759801         & 13.748              \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761956509 &               & 2.761956506       & 4.870              & 0.346              & 4.662992222         & 13.748              \\
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\
        \hline
        $\calT_{C,5}$   & 0.3179254398 & 4.31776537   &                    & 3.246136642  & 91.66905966662563  \\
        \hline
        $\calT_{C,K}$   & 0.3041392027 & 0.3177997026 &                    & 11.03485346 & 3.611339490040196  \\
        \hline
        $\calT_{B,5}$   & 1.022627161  & 7.698889039  &                    & 25.97226447  & 35.96824737574127  \\
        \hline
        $\calT_{B,K}$   & 1.022627161  & 10.10602558  &                    & 53.76320901  & 61.02495966269372  \\
        \hline
        $\calT_{F}$     & 0.7117133306 &              &                    & 325.7340627  & 18796.92616132183  \\
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{K,5}$   & 0.2250062929 & 141.1488115 & 129.5249378629681 & 0.1837655124      & 3.391164992       & 139.7449800105412   \\
        \hline
        $\calT_{C,K}$   & 0.2250695032 & 12.15727753 & 5.099236457042005 & 0.1837881324      & 25.89943821       &  8.30608900893      \\
        \hline
        $\calT_{B,5}$   & 0.3315710272 & 113.0845771 & 482.5669036190229 & 0.2330604743      & 152.8861269       &    \\
        \hline
        $\calT_{B,K}$   & 0.3315710272 & 162.6872182 & 1726.182004903473 & 0.2330604743      & 512.2731352       & 2191.733177984011   \\
        \hline
        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}
